---
title: 'PML Project: Write up'
output: html_document
---
Initialize
================
First of all obtain libraries, open the files and set the seed:

```{r}
library(caret);
mydataTrain = read.csv("d:/pml-training.csv");library(caret);mydataTest = read.csv("d:/pml-testing.csv");
set.seed(32343)
```

Preprocess
================
Now we divide the income data into 10 parts, for training and cross validation:

```{r}
folds <- createFolds(y = mydataTrain$classe, k = 10, list = FALSE)
training <- mydataTrain[folds != 10, ]
test <- mydataTrain[folds == 10, ]
```

Building the model
================

We will take the column 9, 10 and 11 as predictor because as we have been observing, with these columns we obtain better results as predictor:

```{r}
trainingPredictor <- training[, c(9,10,11, 160)]
trainingTestPredictor <- test[, c(9,10,11, 160)]
testingPredictor <- mydataTest[, c(9,10,11, 160)]
```

Training
================

First we need to transform the "classe" column into a factor:

```{r}
trainingPredictor <- transform(trainingPredictor, classe = as.factor(classe))
trainingTestPredictor <- transform(trainingTestPredictor, classe = as.factor(classe))
```

now, we train with the method "rpart":

```{r}
modelFit <- train(classe ~ ., method = "rpart", data = trainingPredictor)
print(modelFit$finalModel)
```

Testing
================

```{r}
prediction1 <- predict(modelFit, newdata = trainingPredictor)
table(prediction1 == trainingPredictor$classe)
table(prediction1 == trainingPredictor$classe)[2]/sum(table(prediction1 == trainingPredictor$classe))
```

Cross Validation
================

```{r}
prediction2 <- predict(modelFit, newdata = trainingTestPredictor)
table(prediction2 == trainingTestPredictor$classe)
table(prediction2 == trainingTestPredictor$classe)[2]/sum(table(prediction2 == trainingTestPredictor$classe))
```

20 different cases prediction
================

```{r}
prediction3 <- predict(modelFit, newdata = testingPredictor)
table(prediction3)
```

Outcome

```{r}
prediction3
```


